Covariate analysis of UFL-Mayo-ISB RNASeq temporal cortex

### 2016-01-30 code/Rmd/Mayo_TemporalCortex_RNASeq.Rmd

@@

p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(color=factor(Diagnosis), shape=as.factor(Source), size=as.numeric(AgeAtDeath)))
p <- p + theme_bw() + theme(legend.position="top") 
# p <- p + geom_text(aes(label= SampleID), size=4, hjust=0)
p
```
```{r decompse.normalise.data4, fig.height=10, fig.width=25, results='asis'}
# Tree based clustering
sampleTrees = flashClust::hclust(dist(t(RESIDUAL.GENE_EXPRESSION[,-(1)])), method = "average")

plotDendroAndColors(sampleTrees, 
                    colors = labels2colors(COVARIATES), 
                    abHeight = 0.80, 
                    main = "Sample dendrogram",
                    groupLabels = colnames(COVARIATES))
collectGarbage()
dev.off()
```

@@

```{r get.gene.symbols}
# Define biomart object
mart <- useMart(biomart = "ensembl", dataset = "hsapiens_gene_ensembl")

@@

DE = ldply(DE, .id = 'Comparison')
tmp = DE %>% 
  dplyr::filter(adj.P.Val <= 0.05) %>%
  group_by(Comparison) %>%
  dplyr::summarize(nDiffExpGenes = length(unique(hgnc_symbol)),
                   DiffExpGenes = paste(unique(hgnc_symbol), collapse = ','))
kable(tmp)
```

>>>>

# Tree based clustering
sampleTrees = flashClust::hclust(dist(t(RESIDUAL.GENE_EXPRESSION[,-(1)])), method = "average")

# Cluster expression
clust = cutreeStatic(sampleTrees, cutHeight = 100, minSize = 10)

# Plot first 2 PCs
plotdata <- data.frame(ID=rownames(PC$rotation), 
                       PC1=PC$rotation[,1], 
                       PC2=PC$rotation[,2],
                       clust = clust)

@@

p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(color=factor(clust), shape=as.factor(Source), size=as.numeric(AgeAtDeath)))
p <- p + theme_bw() + theme(legend.position="top") 
# p <- p + geom_text(aes(label= SampleID), size=4, hjust=0)
p

names(clust) = sampleTrees$labels
clust = clust[rownames(COVARIATES)]
```
```{r decompse.normalise.data4, fig.height=10, fig.width=25, results='asis'}
# Tree based clustering
plotDendroAndColors(sampleTrees, 
                    colors = labels2colors(cbind(data.frame(clust = clust), COVARIATES)), 
                    abHeight = 0.80, 
                    main = "Sample dendrogram",
                    groupLabels = colnames(COVARIATES))
collectGarbage()
dev.off()

writeLines(paste('Samples that deviate from others are', paste(sampleTrees$labels[clust==0], collapse = ',')))
```

@@

```{r get.gene.symbols}
# Define biomart object
mart <- useMart(biomart = "ENSEMBL_MART_ENSEMBL", dataset = "hsapiens_gene_ensembl", host = "www.ensembl.org")

@@

DE = plyr::ldply(DE, .id = 'Comparison')
tmp = DE %>% 
  dplyr::filter(adj.P.Val <= 0.05) %>%
  group_by(Comparison) %>%
  dplyr::summarize(nDiffExpGenes = length(unique(hgnc_symbol)))
kable(tmp)
```
